For the website testing, I have prepared automated unit tests and manual scenarios.
The automated tests are written in the TypeScript programming language using the Jest~\footnote{\url{https://jestjs.io/}} framework.
The manual scenarios serve as a guide for the user testing of the website
and for verifying the correctness of the website's behavior.


\section{Automated Testing}
Using the Jest framework, I have created unit tests for the most critical parts of the website.
The tests cover the services and components of the website.
They are located in the \texttt{\_\_tests\_\_} directory.
The test coverage statistics are in the table~\ref{tab:tests-coverage}.

\begin{table}[hbt!]
    \centering
    \captionsetup{justification=centering}
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        ~        & Statements & Branches & Functions & Lines   \\
        \hline
        Coverage & 97.46\%    & 95.73\%  & 86.74\%   & 97.46\% \\
        \hline
    \end{tabular}
    \caption{Test coverage statistics}
    \label{tab:tests-coverage}
\end{table}


\section{Manual Scenarios}
For the manual user testing of the website, I have created scenarios that cover all use cases.
Each scenario consists of:
\begin{itemize}
    \item initial state,
    \item steps,
    \item covered use cases.
\end{itemize}

In the individual steps, I describe how to achieve the result defined in the title of the testing scenario.

\newcounter{testingcounter}
\newcommand{\testing}[1]{%
    \stepcounter{testingcounter}%
    \subsection{T\arabic{testingcounter} -- #1}
}


\testing{Generating the website from proto files and validating the data}
Initial state: A folder with proto files\\
Steps:
\begin{enumerate}
    \item Open the terminal
    \item Write a command for translating proto files to JSON \textit{gf-proto-to-json \. > common.json}
    \item Open the website (locally or hosted), change the input to file, and upload the JSON file
    \item Check if the data is correctly displayed, including the services, methods, and messages
    \item Check if the comments and options are present
\end{enumerate}
Use cases covered: UC1, UC3, UC4, UC5, UC6, UC7

\testing{Generating the website from the gRPC reflection and validating the data}
Initial state: A gRPC server URL with reflection enabled\\
Steps:
\begin{enumerate}
    \item Open the terminal
    \item Write a command for getting the bin file from the gRPC server \textit{grpcurl -protoset-out descriptors.bin -plaintext \$\{GRPC\_SERVER\_URL\} describe}
    \item Write a command for translating the bin descriptors file to JSON \textit{gf-reflection-to-json descriptors.bin > common.json}
    \item Open the website (locally or hosted), change the input to file, and upload the bin file
    \item Check if the data is correctly displayed, including the services, methods, and messages
    \item Check if the comments and options are present
\end{enumerate}
Use cases covered: UC2, UC3, UC4, UC5, UC6, UC7

\testing{Executing unary request}
Initial state: Hosted website with loaded definitions and gRPC server running with the Envoy proxy\\
Steps:
\begin{enumerate}
    \item Open the website with definitions loaded
    \item Open the unary request
    \item Fill in the required fields
    \item Click on the \enquote{Execute} button
    \item Check if the response is displayed with headers and trailers
\end{enumerate}
Use cases covered: UC8

\testing{Executing server streaming request}
Initial state: Hosted website with loaded definitions and gRPC server running with the Envoy proxy\\
Steps:
\begin{enumerate}
    \item Open the website with definitions loaded
    \item Open the server streaming request
    \item Fill in the required fields
    \item Click on the \enquote{Execute} button
    \item Check if the responses are being displayed as they arrive
    \item Check if the headers and trailers are displayed
\end{enumerate}
Use cases covered: UC9

\testing{Setting global metadata}
Initial state: Hosted website with loaded definitions and gRPC server running with the Envoy proxy\\
Steps:
\begin{enumerate}
    \item Open the website with definitions loaded
    \item Click the metadata button
    \item Set any key-value metadata pair
    \item Set the authorization token
    \item Close the metadata dialog
    \item Open any unary request
    \item Fill in the required fields
    \item Click on the \enquote{Execute} button
    \item Check if the request contains the set metadata
\end{enumerate}
Use cases covered: UC10


\input{text/c_user-testing}


\section{Testing Summary}
The user testing feedback was positive, and the testers found the website intuitive and clear.
It was also appreciated that the process and documentation presentation are familiar to the Swagger UI\@.
The generation of the common format was simple, but it was suggested to have a button for the generation in the UI\@.
The generation is designed to be performed by automatic deployment or other tools, so having the UI would change its purpose.
Therefore, it is not planned to be implemented.

The user testing showed that the resulting website fulfills the documentation purpose and allows the method calls, and does not contain any functionality-affecting bugs.
After fixing the found usability issues (see subsection~\ref{subsec:found-issues-and-their-solutions}), the intuitiveness of the website is met.

The automatic and manual testing confirmed the fulfillment and functionality of all the static website generator requirements.